% !TEX root = endterm_exam_ss2023.tex
% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
\documentclass{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[a4paper,top=2cm,bottom=2cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage{amssymb,amsmath,amsfonts}
\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{booktabs,longtable}
\usepackage{xcolor}
%\parindent0mm
%\parskip1.5ex plus0.5ex minus0.5ex

\begin{document}
	
\title{Computational Macroeconomics}
\author{Endterm Exam}
\date{Summer 2023}
\maketitle


\begin{itemize}
\item
Answer \textbf{all} of the following \textbf{three} exercises in English.
\item
All assignments will be given the same weight in the final grade.
\item
Hand in your solutions before Sunday August, 04 2023 at 3pm.
\item
The solution files should contain your executable (and commented) Dynare and MATLAB files
  as well as all additional documentation as \texttt{pdf}, not \texttt{doc} or \texttt{docx}.
Your \texttt{pdf} files may also include scans or pictures of handwritten notes.
\item
Please e-mail ALL the solution files to \url{willi.mutschler@uni-tuebingen.de}.
I will confirm the receipt of your work also by email (typically within the hour). If not, please resend it to me.
\item
All students must work on their own, please also give your student ID number and the name of the module you want to earn credits for.
\item
It is advised to regularly check Ilias and your emails in case of urgent updates.
\item
If there are any questions, do not hesitate to contact Willi Mutschler.
\end{itemize}

%\section*{Changelog}
\newpage

\section[Technology shocks with non-symmetric innovations]{Technology shocks with non-symmetric innovations\label{ex:Andreasen_2012}}
The goal of this exercise is to look into the third-order perturbation approach and replicate columns (2) and (3) of Table 2 in Andreasen (2012):
  \emph{On the effects of rare disasters and uncertainty shocks for risk premia in non-linear DSGE models},
  published in Review of Economic Dynamics (15).
For the following exercise, we will focus on the sections about rare disasters only.

\begin{enumerate}
\item
What is the main research question of the paper?
Why is the proposed third-order perturbation solution method appropriate to tackle this research question?

\item
Compared to the standard New Keynesian DSGE model we learned about in the lecture,
  what features are added in the paper and why? Do you find the modelling approach of a rare disaster convincing?

\item
The third-order perturbation solution in Dynare's model framework is given by:
\begin{align*}
y_t &= \bar{y}\\
&
\colorbox{gray!10}{\(%
+g_x (x_{t-1} - \bar{x}) + g_u u_{t}
\)}
\\
&
\qquad
\colorbox{gray!10}{\(%
+ g_{\sigma}
\)}
\\
&
\colorbox{gray!25}{\(%
+ \frac{1}{2} g_{xx} \left((x_{t-1} - \bar{x}) \otimes (x_{t-1} - \bar{x})\right)
  +           g_{xu} \left((x_{t-1} - \bar{x}) \otimes u_t\right)
+ \frac{1}{2} g_{uu} \left(u_t \otimes u_t\right)
\)}
\\
&
\qquad
\colorbox{gray!25}{\(%
+ g_{x\sigma} (x_{t-1} - \bar{x})
+ g_{u\sigma} u_t
\)}
\\
&
\qquad\qquad
\colorbox{gray!25}{\(%
+ \frac{1}{2} g_{\sigma\sigma}
\)}
\\
&
\colorbox{gray!50}{\(%
  + \frac{1}{6} g_{xxx} \left((x_{t-1} - \bar{x}) \otimes (x_{t-1} - \bar{x}) \otimes (x_{t-1} - \bar{x})\right)
  + \frac{1}{6} g_{uuu} \left(u_t \otimes u_t \otimes u_t\right)
\)}
\\
&
\qquad
\colorbox{gray!50}{\(%
+ \frac{3}{6} g_{xxu} \left((x_{t-1} - \bar{x}) \otimes (x_{t-1} - \bar{x}) \otimes u_t \right)
+ \frac{3}{6} g_{xuu} \left((x_{t-1} - \bar{x}) \otimes u_t \otimes u_t \right)
\)}
\\
&
\qquad\qquad
\colorbox{gray!50}{\(%
  + \frac{3}{6} g_{xx\sigma} \left((x_{t-1} - \bar{x}) \otimes (x_{t-1} - \bar{x}) \right)
  +             g_{xu\sigma} \left((x_{t-1} - \bar{x}) \otimes u_t \right)
+ \frac{3}{6} g_{uu\sigma} \left(u_t \otimes u_t \right)
\)}
\\
&
\qquad\qquad\qquad
\colorbox{gray!50}{\(%
  + \frac{3}{6} g_{x\sigma\sigma} (x_{t-1} - \bar{x})
  + \frac{3}{6} g_{u\sigma\sigma} u_t
\)}
\\
&
\qquad\qquad\qquad\qquad
\colorbox{gray!50}{\(
  + \frac{1}{6} g_{\sigma\sigma\sigma}
\)}
\end{align*}
where after running \texttt{stoch\_simul{(order=3)}}

\begin{itemize}
\item
\(x_t\) are the state variables and \(y_t\) are the variables that we focus our analysis on (i.e.\ reported or observed variables)

\item
the steady-states \(\bar{x}\) and \(\bar{y}\) can be accessed from the rows of\\
\texttt{oo\_.dr.ys{(oo\_.dr.order\_var)}}

\item
the \colorbox{gray!10}{first-order terms} can be accessed from the rows of\\
\texttt{oo\_.dr.ghx} and \texttt{oo\_.dr.ghu}

\item
the \colorbox{gray!25}{second-order terms} can be accessed from the rows of\\
\texttt{oo\_.dr.ghxx}, \texttt{oo\_.dr.ghxu}, \texttt{oo\_.dr.ghuu}, and \texttt{oo\_.dr.ghs2}

\item
the \colorbox{gray!25}{third-order terms} can be accessed from  the rows of \texttt{oo\_.dr.ghxxx},\\
\texttt{oo\_.dr.ghxxu}, \texttt{oo\_.dr.ghxuu}, \texttt{oo\_.dr.ghxss}, \texttt{oo\_.dr.ghuuu} and \texttt{oo\_.dr.ghuss}

\end{itemize}

Note that there is no \texttt{oo\_.dr.ghs}, \texttt{oo\_.dr.ghxxs}, \texttt{oo\_.dr.ghxus}, \texttt{oo\_.dr.ghuus}, and \texttt{oo\_.dr.ghs3}.

Why does Dynare not compute \(g_{\sigma}\), \(g_{xx\sigma}\), \(g_{xu\sigma}\), \(g_{uu\sigma}\), and \(g_{\sigma\sigma\sigma}\)?
\end{enumerate}

Now consider Table (2) of the paper.

\begin{enumerate}[resume]
\item
Replicate column (2) labeled \emph{Benchmark}. Note that this requires to run a simulation of length 2000000 for a third-order approximation to the model with Gaussian shocks.
In the hints below you will find out how to get the same shock series to replicate the numbers in the column.

\item
Replicate column (3) labeled \emph{Case I}. Note that this requires to run a simulation of length 2000000 for a third-order approximation to the model with non-symmetric shocks.
In the hints below you will find out how to get the same shock series to replicate the numbers in the column.

\item
Comment on the different results obtained in columns (2) and (3) of the table.
\end{enumerate}

\newpage

\subsection*{Codes and hints}

\begin{itemize}
\item
The paper and technical appendix are available on Ilias.

\item
The mod file \texttt{Andreasen\_2012\_rare\_disasters.mod} contains a Dynare version of the DSGE model used to study rare disasters.
This mod file simulates data and computes empirical moments from a simulated time series of length 2000000 for a first-order approximation to the model.
Note that your task is to adapt the codes that do the simulation for a third-order approximation.
The mod file also contains some further hints and explanations.

\item
The function \texttt{Andreasen\_2012\_get\_shocks.m} produces both the Gaussian and non-symmetric shock series used to replicate columns (2) and (3) in Table 2 of the paper.
It also creates \(\Sigma^{(3)}\) for both cases which is an input argument of \texttt{get\_ghs3.m}.

\item
The function \texttt{get\_ghs3.m} computes \(g_{\sigma\sigma\sigma}\) from
\begin{align*}
(A+B) g_{\sigma\sigma\sigma} = -\left( f_{y^{**}_{+}} g^{**}_{uuu} + f_{y^{**}_{+}y^{**}_{+}} (g^{**}_u \otimes g^{**}_{uu})P^3_{u\_uu} + f_{y^{**}_{+}y^{**}_{+}y^{**}_{+}} (g^{**}_u \otimes g^{**}_u \otimes g^{**}_u)\right)\Sigma^{(3)} \label{eq:gsss}
\end{align*}
where \(f_{y^{**}_{+}}\), \(f_{y^{**}_{+}y^{**}_{+}}\), and \(f_{y^{**}_{+}y^{**}_{+}y^{**}_{+}}\) are the first, second, and third-order derivatives of the dynamic model equations with respect to forward jumper variables \(y_{t+1}^{**}\).
\(g^{**}_u\), \(g^{**}_{uu}\), and \(g^{**}_{uuu}\) are the partial derivatives of the jumper variables with respect to shocks.
\(P^3_{u\_uu}\) is a permutation matrix.
\(\Sigma^{(3)} = E[u_t \otimes u_t \otimes u_t]\) are the vectorized unconditional third-order product moments.
\(A\) and \(B\) are the auxiliary perturbation matrices:
\begin{align*}
A & = f_{y_0} + \begin{pmatrix} \underbrace{0}_{n\times n_{static}} &\vdots& \underbrace{f_{y^{**}_{+}} \cdot g^{**}_{x}}_{n \times n_{spred}} &\vdots& \underbrace{0}_{n\times n_{frwd}}  \end{pmatrix}\\
B & = \begin{pmatrix} \underbrace{0}_{n \times n_{static}}&\vdots & \underbrace{0}_{n \times n_{pred}} & \vdots & \underbrace{f_{y^{**}_{+}}}_{n \times n_{sfwrd}} \end{pmatrix}
\end{align*}
where \(f_{y_{0}}\) are the first derivatives of the dynamic model equations with respect to all current endogenous variables \(y_{t}^{}\)
and \(g^{**}_{x}\) are the first partial derivatives of the jumper variables with respect to previous state variables.

\item
In MATLAB, the Kronecker product \(\mathcal{A} \otimes \mathcal{B} \otimes \mathcal{C}\) of arbitrary matrices \(\mathcal{A}\), \(\mathcal{B}\), and \(\mathcal{C}\)
  can be computed using \texttt{kron{(\(\mathcal{A}\),kron{(\(\mathcal{B}\),\(\mathcal{C}\))})}}.

\item
If your computer struggles with the simulation, reduce the length of the simulation to 200000 or lower.
\end{itemize}

\newpage

\section[Solving the RBC model with leisure using a simple projection method]{Solving the RBC model with leisure using a simple projection method\label{ex:RBCLeisureProjection}}
Consider the basic RBC model with leisure and a CES utility function represented by the following system of equations:
\begin{align*}
{{C}}_{t}^{-{{\eta^C}}} &={{\beta}}\, E_t \left \{{{C}}_{t+1}^{-{{\eta^C}}}\, \left(1-{{\delta}}+{{R}}_{t+1}\right) \right \}
\\
{{W}}_{t}&=\frac{\psi \, {\left(1-{{L}}_{t}\right)}^{-{{\eta^L}}}}{{{C}}_{t}^{-{{\eta^C}}}}
\\
{{W}}_{t}&=\left(1-{{\alpha}}\right)\, {{A}}_{t}\, {\left(\frac{{{K}}_{t-1}}{{{L}}_{t}}\right)}^{{{\alpha}}}
\\
{{R}}_{t}&={{\alpha}}\, {{A}}_{t}\, {\left(\frac{{{K}}_{t-1}}{{{L}}_{t}}\right)}^{{{\alpha}}-1}
\\
{{Y}}_{t}&={{A}}_{t}\, {{K}}_{t-1}^{{{\alpha}}}\, {{L}}_{t}^{1-{{\alpha}}}
\\
{{Y}}_{t}&={{C}}_{t}+{{I}}_{t}
\\
{{K}}_{t}&={{I}}_{t}+\left(1-{{\delta}}\right)\, {{K}}_{t-1}
\\
\log\left({{A}}_{t}\right)&={{\rho}}\, \log\left({{A}}_{t-1}\right)+{{\varepsilon}}_{t}
\end{align*}
The description of variables and parameters are given in Tables~\ref{tbl:RBC.Variables} and~\ref{tbl:RBC.Parameters}.
The goal of this exercise is to solve the model with a simple projection method.

\begin{enumerate}
\item
Briefly describe the four steps of the projection method to solve a DSGE model.

\item
What is the \emph{curse of dimensionality}? Does this curse also apply to perturbation methods?

\item
Solve the model using a projection method. To this end:
  \begin{itemize}
  \item
  Set up a simple grid for the state variables \(K_{t-1}\) and \(A_t\):
  \begin{itemize}
    \item For \(K_{t-1}\) use 10 evenly distributed points between \(\frac{1}{2}\bar{K}\) and \(\frac{3}{2}\bar{K}\), where \(\bar{K}\) is the steady-state of \(K_t\).
    \item For \(\log(A_t)\) use 10 evenly distributed points between \(-3\frac{\sigma^2}{1-\rho^2}\) and \(3\frac{\sigma^2}{1-\rho^2}\).
  \end{itemize}

  \item
  Use regular second-order polynomials for approximating the policy functions for the log of consumption and the log of labor supply:
  {\small
  \begin{align*}
    \log(C_t) &= \theta_{1} + \theta_{2} \log{(K_{t-1})} + \theta_{3} \log{(A_t)} + \theta_{4} \log{(K_{t-1})}^2 + \theta_{5} \log{(A_t)}^2 + \theta_{6} \log{(K_{t-1})}\log{(A_t)}
    \\
    \log(L_t) &= \theta_{7} + \theta_{8} \log{(K_{t-1})} + \theta_{9} \log{(A_t)} + \theta_{10} \log{(K_{t-1})}^2 + \theta_{11} \log{(A_t)}^2 + \theta_{12} \log{(K_{t-1})}\log{(A_t)}
  \end{align*}}

  \item
  To minimize the Euler residuals use {\texttt{fminsearch}} with the following set of options:\\
  {\small
  \texttt{optimset{({'MaxFunEvals'},{1e5},{'MaxIter'},{1e6},{'TolFun'},{1e-7},{'TolX'},{1e-7},{'Display'},{'Iter'})}}
  }.
\end{itemize}

\item
Plot both the consumption and labor supply choice as a function of the grid on \(K_{t-1}\) and for 3 values of \(A_t = \{0.9,1.0,1.1\} \).
\end{enumerate}

\newpage

\subsection*{Codes and hints}

\begin{itemize}
\item
A Dynare version of this model is given in the file \texttt{rbc\_ces.mod}.
This file computes the steady-state and a second-order perturbation approximation.
It might contain some useful information or computations for the projection method.
\end{itemize}

\begin{center}
\begin{longtable}{cc}
\caption{Variables}\label{tbl:RBC.Variables}\\%
\toprule%
\multicolumn{1}{c}{\textbf{Variables}} &
\multicolumn{1}{c}{\textbf{Description}}\\%
\midrule\midrule%
\endfirsthead%
\multicolumn{2}{c}{{\tablename} \thetable{} {--} Continued}\\%
\midrule%
\multicolumn{1}{c}{\textbf{Variables}} &
\multicolumn{1}{c}{\textbf{Description}}\\%
\midrule\midrule%
\endhead%
\({Y_t}\) & output\\
\({C_t}\) & consumption\\
\({K_t}\) & capital\\
\({L_t}\) & labor\\
\({A_t}\) & productivity\\
\({R_t}\) & real return on capital\\
\({W_t}\) & real wage\\
\({I_t}\) & investment\\
\({\varepsilon_t}\) & Productivity Shock\\
\bottomrule%
\end{longtable}
\end{center}

\begin{center}
\begin{longtable}{ccc}
\caption{Parameters}\label{tbl:RBC.Parameters}\\%
\toprule%
\multicolumn{1}{c}{\textbf{Parameter}} &
\multicolumn{1}{c}{\textbf{Value}} &
\multicolumn{1}{c}{\textbf{Description}}\\%
\midrule%
\endfirsthead%
\multicolumn{3}{c}{{\tablename} \thetable{} {--} Continued}\\%
\midrule%
\multicolumn{1}{c}{\textbf{Parameter}} &
\multicolumn{1}{c}{\textbf{Value}} &
\multicolumn{1}{c}{\textbf{Description}}\\%
\midrule%
\endhead%
\({\alpha}\) 	 & 	 0.350 	 & 	 Output Elasticity of Capital\\
\({\beta}\) 	 & 	 0.990 	 & 	 Discount Factor\\
\({\delta}\) 	 & 	 0.025 	 & 	 Depreciation Rate\\
\({\rho}\) 	   & 	 0.900 	 & 	 Persistence technology\\
\({\bar{L}}\)  & 	 0.333 	 & 	 steady-state labor that calibrates \(\psi \) endogenously\\
\({\eta^C}\) 	 & 	 2.000 	 & 	 CES utility elasticity with respect to consumption\\
\({\eta^L}\) 	 & 	 1.500 	 & 	 CES utility elasticity with respect to labor\\
\({\psi}\) 	   & 	 \(\bar{W}{(1-\bar{L})}^{\eta_L} \bar{C}^{-\eta_C}\) 	 & 	the labor disutility weight, where \(\bar{W}\) and \(\bar{C}\) \\
               &           &are the steady-states of \(W_t\) and \(C_t\)
\\
\bottomrule%
\end{longtable}
\end{center}

\newpage

\section{Comparison between perturbation and projection methods}
Consider the handbook chapter of Fernandez-Villaverde, Rubio-Ramirez, and Schorfheide (2016) {--} Solution and Estimation Methods for DSGE Models.

\begin{enumerate}
\item
Explain the strengths and weaknesses of perturbation and projection methods in your own words.

\item
How can we assess the accuracy of a numerical solution method for a DSGE model?
\end{enumerate}

\end{document}
