\section[ARMA{(1,1)} Simulation]{ARMA{(1,1)} Simulation\label{ex:ARMASimulation}}
Consider the ARMA{(1,1)} model:
\begin{align*}
x_t - \theta x_{t-1} = \varepsilon_t - \phi \varepsilon_{t-1}
\end{align*}
where \(\varepsilon_t \sim N(0,1)\).

\begin{enumerate}

\item
Compute the non-stochastic steady-state with pen and paper,
  i.e.\ what is the value of \(x_t\) if \(\varepsilon_t = 0\) for all \(t\)?

\item
Write a Dynare mod file for this model:

\begin{itemize}

\item
\(x\) is the endogenous variable, \({\varepsilon}\) the exogenous variable, and \({\theta}\) and \({\phi}\) are the parameters.

\item
Set \(\theta = \phi = 0.4\).

\item
Write either a \texttt{steady\_state\_model} or \texttt{initval} block and compute the steady-state.

\item
Start at the non-stochastic steady-state and simulate 200 data points using a \texttt{shocks} block
  and the \texttt{stoch\_simul} command.
Plot both \(x\) as well as \({\varepsilon}\) using \texttt{rplot}.

\item
Try out different values for \({\theta}\) and \({\phi}\).
What do you notice?

\end{itemize}

\item
Redo the exercise in MATLAB without using Dynare.

\end{enumerate}

\emph{Hints}:

\begin{itemize}

\item
Don't forget to add Dynare's matlab folder:
\texttt{addpath C:/dynare/6.0/matlab} for Windows,
\texttt{addpath /Applications/Dynare/6.0/matlab} for macOS,
\texttt{addpath /opt/dynare/6.0/matlab} for Linux machines.
If you installed Dynare to a different folder, adapt the path accordingly.

\item
When saving your Dynare script as a mod file, try to use a simple name.
That is, don't use special characters or spaces in the filename, e.g.\
  \texttt{arma{(1,1)}.mod} as well as \texttt{arma 1 1.mod} are not valid filenames,
  whereas \texttt{arma.mod} or \texttt{arma\_1\_1.mod} or \texttt{arma11.mod} are valid.

\item
It is advised to save the mod file directly on your hard drive and not on a cloud storage drive.
If you do save it to a folder that is in sync with e.g.\ Dropbox, iCloud, Nextcloud, OneDrive (etc),
  please (temporarily) deactivate sync activities,
  to prevent sync conflicts and weird errors when running Dynare.

\end{itemize}


\begin{solution}\textbf{Solution to \nameref{ex:ARMASimulation}}
\ifDisplaySolutions%
\input{exercises/arma_simulation_solution.tex}
\fi
\newpage
\end{solution}