\section[Case Study Eichenbaum, Rebelo and Trabandt (2022, JEDC): Epidemics in the New Keynesian model]{Case Study Eichenbaum, Rebelo and Trabandt (2022, JEDC): Epidemics in the New Keynesian model\label{ex:CaseStudy.Eichenbaum.Rebelo.Trabandt.2022}}

\begin{enumerate}
\item Read the paper by \textcite{Eichenbaum.Rebelo.Trabandt_2022_EpidemicsNewKeynesian}
  and focus particularly on Section 3 (The model economy), Section 4 (The impact of an epidemic), and the Appendix A (Equilibrium equations).

\item Consider the Dynare mod file given in Appendix \ref{app:ert_model_sticky}, which is a stripped down version of the sticky-price New Keynesian SIR model as outlined in Appendix A of the paper.
Compute the steady-state using an \texttt{initval} block.

\item Note that the mod file contains a \texttt{predetermined\_variables} command.
Read about this in the manual of Dynare \parencite{Adjemian.Bastani.Juillard.EtAl_2022_DynareReferenceManual}
  and explain why this is relevant in the current model.

\item Note that the Taylor rule, in equation 31), exhibits differences between the mod file and the paper.
Specifically, in the paper, the output gap is defined as the discrepancy between output and the corresponding output level under flexible prices ($\xi=0$),
  whereas in the mod file, it is defined as deviations from the steady-state.
Generate a new mod file that incorporates equations for both the sticky-price and flexible-price economies,
  with the two models connected through the Taylor rule in the sticky model.
Additionally, you need to recalculate the pre-infectious steady-state for the combined economies.
\emph{Hint: Don't forget to set the macro directive by including:\\ \texttt{\@\#define FLEX\_PRICE\_OUTPUT\_GAP = 1}}

\item Read section \texttt{4.7. Initial and terminal conditions} in the manual of Dynare \parencite{Adjemian.Bastani.Juillard.EtAl_2022_DynareReferenceManual}.
Add a \texttt{histval} block that implements the impact of an epidemic in the model,
  i.e. in period $t=0$ change infected to $i_0=\varepsilon$ and susceptibles to $s_0=1-\varepsilon$,
  while all other variables are set to their pre-infection steady-state.
Run \texttt{perfect\_foresight\_setup} and have a look how Dynare initializes \texttt{M\_.\_endo\_histval},
  \texttt{oo\_.\_endo\_simul} and \texttt{oo.\_exo\_simul} for the Newton algorithm.

\item Notice that the \texttt{model} block has a \texttt{differentiate\_forward\_vars} option.
Look into the manual of Dynare \parencite{Adjemian.Bastani.Juillard.EtAl_2022_DynareReferenceManual} what this option does.
Explain why it is necessary in this model when we want to simulate the impact of an epidemic?

\item What is \emph{homotopy} in the context of perfect foresight simulations?
Illustrate this by setting
\begin{align*}
\pi_1 &= 2.568436063602094 \times 10^{-7}\\
\pi_2 &= 1.593556989906377  \times 10^{-4}\\
\pi_3 &= 0.499739472034583
\end{align*}
  and running a perfect foresight solver using the above \texttt{histval} block.

\newpage

\item Simulate the economy when the epidemic is a shock to consumption demand only,
  i.e.\ replicate Figures 5 and 6.
To this end, calibrate the probabilities according to:

{\footnotesize
\begin{lstlisting}[style=Matlab-editor,basicstyle=\mlttfamily\scriptsize]
% calibation targets for shares of pi-terms in T-function in SIR model
pi3_shr_target = 2/3;                  % share of T_0 jump due general infections
pi1_shr_target = (1-pi3_shr_target);   % share of T_0 jump due to consumption-based infections
pi2_shr_target = 0;                    % share of T_0 jump due to work-based infections
[pi1_final,pi2_final,pi3_final] = ert_model_go_calibrate_pi(250,varepsilon,pir,pid,pi1_shr_target,pi2_shr_target,RplusD_target,c_ss,n_ss);
\end{lstlisting}
}

\item Simulate the economy when the epidemic is a shock to labor supply only,
  i.e.\ replicate Figures 7 and 8.
To this end, calibrate the probabilities according to:

{\footnotesize
\begin{lstlisting}[style=Matlab-editor,basicstyle=\mlttfamily\scriptsize]
pi3_shr_target = 2/3;                  % share of T_0 jump due general infections
pi1_shr_target = 0;                    % share of T_0 jump due to consumption-based infections
pi2_shr_target = (1-pi3_shr_target);   % share of T_0 jump due to work-based infections
[pi1_final,pi2_final,pi3_final] = ert_model_go_calibrate_pi(250,varepsilon,pir,pid,pi1_shr_target,pi2_shr_target,RplusD_target,c_ss,n_ss);
\end{lstlisting}
}

\item Simulate the economy when the epidemic is a shock to both consumption demand and labor supply,
  i.e.\ replicate Figures 9 and 10.
To this end, calibrate the probabilities according to:

{\footnotesize
\begin{lstlisting}[style=Matlab-editor,basicstyle=\mlttfamily\scriptsize]
pi3_shr_target = 2/3;                  % share of T_0 jump due general infections
pi1_shr_target = (1-pi3_shr_target)/2; % share of T_0 jump due to consumption-based infections
pi2_shr_target = (1-pi3_shr_target)/2; % share of T_0 jump due to work-based infections
[pi1_final,pi2_final,pi3_final] = ert_model_go_calibrate_pi(250,varepsilon,pir,pid,pi1_shr_target,pi2_shr_target,RplusD_target,c_ss,n_ss);
\end{lstlisting}
}
    
\end{enumerate}


\paragraph{Hints}

\begin{itemize}

\item Appendix \ref{app:ert_model_go_calibrate_pi} contains a helper function to calibrate the probabilities $\pi_1$, $\pi_2$ and $\pi_3$.
    
\item Appendix \ref{app:ert_model_plot_agg_results} contains a helper function to plot figures 5, 7, and 9.

\item Appendix \ref{app:ert_model_plot_by_type_results} contains a helper function to plot figures 6, 8, and 10.

\item It might help to know that you can have multiple \texttt{model} and \texttt{var} blocks in the same mod file.

\item Dynare's \texttt{\@\#include "SOMEMODILE"} directive might be useful.

\item \texttt{set\_param\_value('pi3',pi3\_final)} is a useful function to update parameters when you loop over parameters.

\item If your solution does not converge, try homotopy for $\pi_3$, e.g. start with $\pi_3/3$.

\item Set the \texttt{periods} option to 500 and the \texttt{maxit} option to 100.

\end{itemize}


\begin{solution}\textbf{Solution to \nameref{ex:CaseStudy.Eichenbaum.Rebelo.Trabandt.2022}}
\ifDisplaySolutions
\input{exercises/case_study_eichenbaum_rebelo_trabandt_2022_solution.tex}
\fi
\newpage
\end{solution}