\section[Numerical optimization in MATLAB]{Numerical optimization in MATLAB\label{ex:MatlabNumericalOptimization}}

\begin{enumerate}

\item
In a nutshell, what is the goal of numerical optimization?

\item
What is an \emph{objective function}, what are \emph{decision or design variables}, what is a \emph{gradient}, and what is a \emph{constraint}?

\item
What is the general idea behind gradient-based optimization algorithms?

\item
What is the general idea behind gradient-free optimization algorithms? Name a few examples.

\item
In numerical optimization theory, the Rosenbrock function is a non-convex function
  often used as a performance test problem for optimization algorithms.
It is defined by:
\begin{align*}
f(x,y) = 100{(y-x^2)}^2 + {(1-x)}^2
\end{align*}
The global minimum is inside a long, narrow, parabolic shaped flat valley.
To find the valley is trivial;
  to converge to the global minimum, however, is difficult.

  \begin{enumerate}

  \item
  Make a 3D plot of the function to see that the global minimum is at \((x, y)=(1, 1)\) where \(f(x, y)=0\).
  \begin{lstlisting}[style=Matlab-editor,basicstyle=\mlttfamily\scriptsize]
  fsurf(@(x,y) ((1-x).^2)+(100*((y-(x.^2)).^2)),[-2 2 -2 5],'ShowContours','on')
  title('Rosenbrock function')
  xlabel('x')
  ylabel('y')
  \end{lstlisting}

  \item
  Find the global minimum of the function by trying out different optimizers.
  Draw the initial values randomly (e.g.\ with \texttt{randi}).

  \end{enumerate}

\item
In numerical optimization theory, the Rastrigin function is a non-convex function
  often used as a performance test problem for optimization algorithms.
It is a typical example of a non-linear multi-modal function and given by:
\begin{align*}
f(x,y) = 20 + x^2 + y^2 - 10(\cos(2\pi x)+\cos(2\pi y))
\end{align*}
Note that the global minimum is at \((x, y)=(0, 0)\) where \(f(x, y)=0\).
Finding the minimum of this function is a fairly difficult problem
  due to its large search space and its large number of local minima.
Repeat the previous exercise on the Rastrigin function.
\end{enumerate}


\paragraph{Readings}
\begin{itemize}
\item AlphaOpt: Introduction to Optimization: What Is Optimization?\\
\url{https://youtu.be/Q2dewZweAtU?si=qGu_NpNSbM9yuAdR}
\item MathWorks: Comparison of Six Solvers\\
\url{https://mathworks.com/help/gads/example-comparing-several-solvers.html}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:MatlabNumericalOptimization}}
\ifDisplaySolutions%
\input{exercises/numerical_optimization_solution.tex}
\fi
\newpage
\end{solution}